# Project Information

## Background

The **Portfolio Insights** project was initiated to facilitate decision making using data driven methodologies based on analytics as against a metrics based approach based used to track project compliance to the triple constraints of cost, time and scope. The focus is on delivery unit performance and diagnostics which is the bed rock for _agile organizations_ as against compliance to a plan and control against the [triple constraint](https://www.pmi.org/learning/library/triple-constraint-erroneous-useless-value-8024).

## Vision

The vision is to have one unified view of data across all enterprise systems. These systems at this point are [Aha!](https://www.aha.io/) used for roadmapping, requirements elaboration and investments, [Atlassian Jira](https://www.atlassian.com/software/jira) and OpenAir. 

## Roadmap

```{r portfolio-insights-roadmap, include=TRUE, echo=FALSE}
  roadmap_df <- read.csv2("var/portfolio-insights-roadmap.csv", sep=',',
                          header=TRUE)
  knitr::kable(roadmap_df)
```

## Stakeholders


### Key Stakeholders

```{r stakeholder-register, include=TRUE, echo=FALSE}
  stakeholders_df <- read.csv2("var/stakeholder-register.csv", sep=',',
                          header=TRUE)
  knitr::kable(stakeholders_df)
```

### Target Users


```{r target-users, include=TRUE, echo=FALSE}
  targetusers_df <- read.csv2("var/target-users.csv", sep=',',
                          header=TRUE)
  knitr::kable(targetusers_df)
```
