## Delivery Metrics 

```{r opics-setup, include=FALSE}
source("./R/common.R")
```

```{r opics-delivery-setup, include=FALSE}

# Create the tibble
tib.all <-
  finmetrics::get.FilteredTibble(here::here("inst/extdata",
                                            "opics_delivery.csv"),
                                 date_from = Sys.Date() - months(18))

tib.all$Priority <- 
  factor(tib.all$Priority, 
                           levels=c("Critical",
                                    "High", 
                                    "Medium", 
                                    "Low", 
                                    "None"), 
                           ordered = TRUE)

tib <- tib.all %>%
  finmetrics::exclude.OpenCases() %>% 
  finmetrics::compute.CycleTime() %>%
  finmetrics::compute.Week()

# Taking a one year subset after calculating cycle time for 18 months.
tib <- tib %>% filter(crdt > Sys.Date() - months(12))

# Collecting only stories, filtering out abnormalities
stories.closed <- tib %>% filter(cldt > crdt) %>% filter(Type == "Story")
# Collecting only Epics, filtering out abnormalities
epics.closed <- tib %>% filter(cldt > crdt) %>% filter(Type == "Epic")


```

###  Cycle Time


#### Summary

The below [Five-number summary](https://en.wikipedia.org/wiki/Five-number_summary) will provide a high level distribution of the cycle times. 

```{r opics-cycle-time-summ, include=TRUE, out.width='80%', echo=FALSE}
tabulate.TypeAndPriorityBasedCycleTimeStat(tib)
```

#### Epics


```{r opics-epics-cycle-time-trend-fig, include=TRUE, out.width='80%', fig.asp=.75, fig.align='center', fig.cap="Cycle Time Trend", echo=FALSE}
loess_plot.CycleTimeTrend(epics.closed, col_date="crdt")

```


```{r opics-epics-summary-metrics, include=TRUE, out.width='80%', echo=FALSE}
 tabulate.PriorityBasedCycleTimeStat(epics.closed)
```

#### Stories

```{r opics-stories-cycle-time-trend-fig, include=TRUE, out.width='80%', fig.asp=.75, fig.align='center', fig.cap="Cycle Time Trend", echo=FALSE}

loess_plot.CycleTimeTrend(stories.closed, col_date="crdt")

```


```{r opics-story-summary-metrics, include=TRUE, out.width='80%', echo=FALSE}

tabulate.PriorityBasedCycleTimeStat(stories.closed)

```

### Throughput

#### Epics

```{r opics-completed-epics-week-fig, out.width='80%', fig.asp=.75, fig.align='center', fig.cap = "Closed Epics by Week", echo=FALSE}

line_plot.NumClosed_For_FloorDate(
  gen_ds.NumClosed_For_FloorDate(epics.closed)
)

```

The plot below shows the number of epics closed in every week, marked separately in different color based on priority

```{r opics-epics-wk-agg-fig, include=TRUE, out.width='80%', fig.asp=.75, fig.align='center', echo=FALSE}

bar_plot.NumClosed_For_FloorDate(
  gen_ds.NumClosed_For_FloorDate(epics.closed, priority_based=TRUE),
  data_values = TRUE
)

```

- Density distribution

Gives and indication of the densities especially the occurrence of multiple maxima in the data. This can be due to multiple categories of work items which may be investigated further. 

```{r opics-density-distibution-closed-epics-fig, include=TRUE, echo=FALSE, out.width="80%", fig.align="center", fig.asp=.75, fig.cap="Priority based Density Distribution", message=FALSE, warning=FALSE}
epics.closed %>% violin_plot.CycleTimeVsPriority()
```


#### Stories


Tells us the number of work items (stories) completed aggregated for each 
week which is an indication of how stable the throughput is.

```{r opics-completed-items-week-fig, out.width='80%', fig.asp=.75, fig.align='center', echo=FALSE}

line_plot.NumClosed_For_FloorDate(
  gen_ds.NumClosed_For_FloorDate(stories.closed), 
  show_trend = TRUE
)

```

The plot below shows the number of stories closed in every week, marked separately in different color based on priority


```{r opics-stories-wk-agg-fig, include=TRUE, out.width='80%', fig.asp=.75, fig.align='center', fig.cap="Number of Stories Closed in a Week colored by Priority", echo=FALSE}

bar_plot.NumClosed_For_FloorDate(
  gen_ds.NumClosed_For_FloorDate(stories.closed, priority_based=TRUE),
  data_values = TRUE
)

```

- Density distribution

Gives and indication of the densities especially the occurrence of multiple maxima in the data. This can be due to multiple categories of work items which may be investigated further. 

```{r opics-density-distibution-closed-stories-fig, include=TRUE, echo=FALSE, out.width="80%", fig.align="center", fig.asp=.75, fig.cap="Priority based Density Distribution", message=FALSE, warning=FALSE}

stories.closed %>% violin_plot.CycleTimeVsPriority()

```


### Flow

#### Work in Progress (WiP)

##### Epics 

```{r opics-epics-work-in-progress, include=TRUE, echo=FALSE}
tib_epics_work_in_progress <- tib.all %>%
  dplyr::filter(Type == 'Epic') %>% finmetrics::compute.WIP()

```

```{r opics-epics-work-in-progress-fig , include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.cap="WiP in Days", fig.align='center', cache=TRUE}
areaPlot.WiP(tib_epics_work_in_progress)
```

##### Stories

```{r opics-stories-work-in-progress, include=TRUE, echo=FALSE}
tib_stories_work_in_progress <- tib.all %>%
  dplyr::filter(Type == 'Story') %>% finmetrics::compute.WIP()

```

```{r opics-stories-work-in-progress-fig , include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.cap="WiP in Days", fig.align='center', cache=TRUE}
areaPlot.WiP(tib_stories_work_in_progress)
```

#### Inflow/OutFlow

##### Epics

```{r opics-epics-inflow-outflow, include=TRUE, echo=FALSE, out.width='80%', fig.align="center", fig.asp=.75, eval=TRUE}
flow.epics.merged <- tib.all %>%
  get.InflowOutflowTibble.Epic(include_priority = TRUE)
 bar_plot.InflowOutflow(flow.epics.merged)
```

```{r opics-epics-inflow-outflow-cumsumm, include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.align="center", eval=TRUE}
line_plot.InflowOutflow.CumSum(flow.epics.merged)
```

```{r opics-epics-inflow-outflow-cumsumm-interactive, include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.align="center", eval=TRUE}
line_plotly.InflowOutflow.CumSum(flow.epics.merged)
```

```{r opics-epics-inflow-outflow-datatable, include=TRUE, echo=FALSE, out.width='80%',fig.asp=.75, fig.align="center", eval=TRUE }
DT::datatable(flow.epics.merged, filter='top')
```
##### Stories

```{r opics-stories-inflow-outflow, include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.align='center',  eval=TRUE}
flow.stories.merged <- tib.all %>%
  get.InflowOutflowTibble.Story(include_priority = TRUE)
 bar_plot.InflowOutflow(flow.stories.merged, data_values = TRUE)
```

```{r opics-stories-inflow-outflow-cumsumm, out.width='80%', fig.asp=.75, fig.align='center',include=TRUE, echo=FALSE, eval=TRUE}
line_plot.InflowOutflow.CumSum(flow.stories.merged)
```
