## Delivery Metrics 

```{r trk-setup, include=FALSE}
# Empty

```

```{r trk-delivery-setup, include=FALSE}

# Create the tibble
tib.all <-
  finmetrics::get.FilteredTibble(here::here("inst/extdata",
                                            "trk_delivery.csv"),
                                 date_from = Sys.Date() - months(18))

tib.anom <- anomalities(tib.all, action = 'SELECT')
tib.all <- anomalities(tib.all, action = 'REJECT')

tib.all$Priority <- 
  factor(tib.all$Priority, 
                           levels=c("Critical",
                                    "High", 
                                    "Medium", 
                                    "Low", 
                                    "None"), 
                           ordered = TRUE)


tib <- tib.all %>%
  finmetrics::exclude.OpenCases() %>% 
  finmetrics::compute.CycleTime() %>%
  finmetrics::compute.Week()

# Taking a one year subset after calculating cycle time for 18 months.
tib <- tib %>% filter(crdt > Sys.Date() - months(18))

# Collecting only stories, filtering out abnormalities
stories.closed <- tib %>% filter(cldt > crdt) %>% filter(Type == "Story")
# Collecting only Epics, filtering out abnormalities
epics.closed <- tib %>% filter(cldt > crdt) %>% filter(Type == "Epic")


```

### Overview 

#### Distribution of priorities across projects

The [Tree Map](https://en.wikipedia.org/wiki/Treemapping) of the entire dataset
provides an excellent solution level overview of the total number of 
work items (Stories) that flowed in across different projects and priorities.


```{r trk-stories-summary-treemap-data, include=FALSE, echo=FALSE}

tib_stories_treemap <- tib.all %>% 
  filter(Type == 'Story') %>%
  group_by(Project, Priority) %>% 
  summarize(Count= n(), .groups = 'drop' )

```

```{r trk-stories-summary-treemap-fig, include=TRUE, out.width='80%', fig.asp=.75, fig.align='center', fig.cap="Summary Tree Map", echo=FALSE, message = FALSE}

treemap_d3(tib_treemap = tib_stories_treemap, title = "Distribution of priorities across projects")

```


###  Cycle Time


#### Summary

The below [Five-number summary](https://en.wikipedia.org/wiki/Five-number_summary) 
will provide a high level distribution of the cycle times. 
The 75% Qartile value is significant because that is the number which you can 
typically see as the turn around time (TAT) to service a work item.

```{r trk-cycle-time-summ, include=TRUE, out.width='80%', echo=FALSE}

tabulate.TypeAndPriorityBasedCycleTimeStat(tib)

```

#### Epics


```{r trk-epics-cycle-time-trend-fig, include=TRUE, out.width='80%', fig.asp=.75, fig.align='center', fig.cap="Cycle Time Trend", echo=FALSE}
loess_plot.CycleTimeTrend(epics.closed, col_date="crdt")
```


```{r trk-epics-summary-metrics, include=TRUE, out.width='80%', echo=FALSE}
 tabulate.PriorityBasedCycleTimeStat(epics.closed)
```

#### Stories

```{r trk-stories-cycle-time-trend-fig, include=TRUE, out.width='80%', fig.asp=.75, fig.align='center', fig.cap="Cycle Time Trend", echo=FALSE}

loess_plot.CycleTimeTrend(stories.closed, col_date="crdt")

```


```{r trk-story-summary-metrics, include=TRUE, out.width='80%', echo=FALSE}

tabulate.PriorityBasedCycleTimeStat(stories.closed)

```

### Throughput

#### Epics

```{r trk-completed-epics-week-fig, out.width='80%', fig.asp=.75, fig.align='center', fig.cap = "Closed Epics by Week", echo=FALSE}

line_plot.NumClosed_For_FloorDate(
  gen_ds.NumClosed_For_FloorDate(epics.closed)
)

```

The plot below shows the number of epics closed in every week, marked separately in different color based on priority

```{r trk-epics-wk-agg-fig, include=TRUE, out.width='80%', fig.asp=.75, fig.align='center', echo=FALSE}

bar_plot.NumClosed_For_FloorDate(
  gen_ds.NumClosed_For_FloorDate(epics.closed, priority_based=TRUE),
  data_values = TRUE
)

```

- Density distribution

Gives and indication of the densities especially the occurrence of multiple maxima in the data. This can be due to multiple categories of work items which may be investigated further. 

```{r trk-density-distibution-closed-epics-fig, include=TRUE, echo=FALSE, out.width="80%", fig.align="center", fig.asp=.75, fig.cap="Priority based Density Distribution", message=FALSE, warning=FALSE}
epics.closed %>% violin_plot.CycleTimeVsPriority()
```


#### Stories


Tells us the number of work items (stories) completed aggregated for each 
week which is an indication of how stable the throughput is.

```{r trk-completed-items-week-fig, out.width='80%', fig.asp=.75, fig.align='center', echo=FALSE}

line_plot.NumClosed_For_FloorDate(
  gen_ds.NumClosed_For_FloorDate(stories.closed), 
  show_trend = TRUE
)

```

The plot below shows the number of stories closed in every week, marked separately in different color based on priority


```{r trk-stories-wk-agg-fig, include=TRUE, out.width='80%', fig.asp=.75, fig.align='center', fig.cap="Number of Stories Closed in a Week colored by Priority", echo=FALSE}

bar_plot.NumClosed_For_FloorDate(
  gen_ds.NumClosed_For_FloorDate(stories.closed, priority_based=TRUE),
  data_values = TRUE
)

```

- Density distribution

Gives and indication of the densities especially the occurrence of multiple maxima in the data. This can be due to multiple categories of work items which may be investigated further. 

```{r trk-density-distibution-closed-stories-fig, include=TRUE, echo=FALSE, out.width="80%", fig.align="center", fig.asp=.75, fig.cap="Priority based Density Distribution", message=FALSE, warning=FALSE}

stories.closed %>% violin_plot.CycleTimeVsPriority()

```


### Flow

#### Work in Progress (WiP)

##### Epics 

```{r trk-epics-work-in-progress, include=TRUE, echo=FALSE}
tib_epics_work_in_progress <- tib.all %>%
  dplyr::filter(Type == 'Epic') %>% finmetrics::compute.WIP()

```

```{r trk-epics-work-in-progress-fig , include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.cap="WiP in Days", fig.align='center', cache=TRUE}
areaPlot.WiP(tib_epics_work_in_progress)
```

##### Stories

```{r trk-stories-work-in-progress, include=TRUE, echo=FALSE}
tib_stories_work_in_progress <- tib.all %>%
  dplyr::filter(Type == 'Story') %>% finmetrics::compute.WIP()

```

```{r trk-stories-work-in-progress-fig , include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.cap="WiP in Days", fig.align='center', cache=TRUE}
areaPlot.WiP(tib_stories_work_in_progress)
```

#### Inflow/OutFlow

##### Epics

```{r trk-epics-inflow-outflow, include=TRUE, echo=FALSE, out.width='80%', fig.align="center", fig.asp=.75, eval=TRUE}
flow.epics.merged <- tib.all %>%
  get.InflowOutflowTibble.Epic(include_priority = TRUE)
 bar_plot.InflowOutflow(flow.epics.merged)
```

```{r trk-epics-inflow-outflow-cumsumm, include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.align="center", eval=TRUE}
line_plot.InflowOutflow.CumSum(flow.epics.merged)
```

```{r trk-epics-inflow-outflow-cumsumm-interactive, include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.align="center", eval=TRUE}
line_plotly.InflowOutflow.CumSum(flow.epics.merged)
```

```{r trk-epics-inflow-outflow-datatable, include=TRUE, echo=FALSE, out.width='80%',fig.asp=.75, fig.align="center", eval=TRUE }
DT::datatable(flow.epics.merged, filter='top')
```
##### Stories

```{r trk-stories-inflow-outflow, include=TRUE, echo=FALSE, out.width='80%', fig.asp=.75, fig.align='center',  eval=TRUE}
flow.stories.merged <- tib.all %>%
  get.InflowOutflowTibble.Story(include_priority = TRUE)
 bar_plot.InflowOutflow(flow.stories.merged, data_values = TRUE)
```

```{r trk-stories-inflow-outflow-cumsumm, out.width='80%', fig.asp=.75, fig.align='center',include=TRUE, echo=FALSE, eval=TRUE}
line_plot.InflowOutflow.CumSum(flow.stories.merged)
```
